#RepData peer Assesssment 1
========================================================

##Loading and preprocessing the data
load data from activity.csv
```{r}
data <- read.csv("activity.csv")
head(data)
asDate <- strptime(data$date, "%Y-%m-%d")
newData <- cbind(data, asDate)
activity <- data.frame(newData$steps , newData$asDate, newData$interval)
names(activity) <- c("steps", "date", "interval")
```

##What is mean total number of steps taken per day?
remove NA value
```{r}
good <- complete.cases(activity)
completeData <- activity[completeData,]
totalSteps <- tapply(activity$steps, activity$date, sum)
```
draw histogram of total steps
```{r}
hist(totalSteps, col = "red", xlab = "Total Steps per Day", ylab = "Frequency", 
     main = "total steps by date")
mean <- mean(completeData$steps)
mean
median <- median(completeData$steps)
median
```
##What is the average daily activity pattern?
Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
stepsInterval<-aggregate(steps~interval,data=activity, FUN=mean, na.rm=TRUE)
head(stepsInterval)
plot(steps~interval,data=stepsInterval,type="l")
```
Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
max <- max(stepsInterval$steps)
max
```

##Imputing missing values
calculate total number of missing data
```{r}
sum(is.na(activity))
missingNum <- length(which(is.na(activity$steps)))
```

Devise a strategy for filling in all of the missing values in the dataset. 
Use the mean for that 5-minute interval
```{r}
stepFit <- function(interval) {
        stepsInterval[stepsInterval$interval == interval, ]$steps
}

newDataset <- activity 
count = 0 
for (i in 1:nrow(newDataset)) {
        if (is.na(newDataset[i, ]$steps)) {
                newDataset[i, ]$steps <- stepFit(newDataset[i, ]$interval)
                count = count + 1
        }
}
newTotalSteps <- aggregate(steps ~ date, data = newDataset, sum)
head(newTotalSteps)
hist(newTotalSteps$steps, main = "Filled value histogram", xlab = "steps")
```
Calculate and report the mean and median total number of steps taken per day
```{r}
mean(newTotalSteps$steps)
median(newTotalSteps$steps)
```

#Are there differences in activity patterns between weekdays and weekends?
Create a new factor variable in the dataset with two levels -- "weekday" and "weekend" indicating whether a given date is a weekday or weekend day.
weekdays(newDataset$date)
```{r}
newDataset$weektime <- as.factor(ifelse(weekdays(newDataset$date) %in% c("Saturday","Sunday"),
                             "weekend", "weekday"))
```
Make a panel plot containing a time series plot 
```{r}
stepsInterval2 = aggregate(steps ~ interval + weektime, newDataset, mean)
library(lattice)
xyplot(steps ~ interval | factor(weektime), data = stepsInterval2, aspect = 1/2, 
       type = "l")
```
